% Thesis Acknowledgements ------------------------------------------------


%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
%\begin{acknowledgements}      %this creates the heading for the acknowlegments

\section*{Acknowledgement} %this results in an overhead bar,  
\pagestyle{empty} %this removes the bar
%\addcontentsline{toc}{chapter}{Acknowledgement}

\epigraph{\textit{``Not many appreciate the ultimate power and potential usefulness of basic knowledge accumulated by obscure, unseen investigators who, in a lifetime of intensive study, may never see any practical use for their findings but who go on seeking answers to the unknown without thought of financial or practical gain.''}}%
{\textit{}\\ \textsc{Eugenie Clark}}

\onehalfspacing

Before anything, I would like to express my gratitude towards my family, specifically my wife, my parents and my kids,
  whose constant love and unconditional support I have greatly relied upon. 
Their immeasurable sacrifices together with their continuous encouragement have always been the motivation for me to follow this academic pursuit.
%venture further. 
%It is ultimately to them that this work is dedicated.
They are the first and foremost people that this work is dedicated upon.

This thesis would also not have been possible without the patient and helpful guidance of Professor Ian McLoughlin and Associate Professor Nicholas Vun Chan Hua, 
	under whose supervision I am gratefully under. 
The supervisors have provided firm support, as well as spot-on guidance. 
During all the stages of my research work, 
	be it conceptualization or result analysis, be it writing, presentation or publishing ..
	their kind attention and wise advice command my utmost respect and admiration.

%The author also wish to thank Dr. Timo Brestchneider and Dr. Lee Ken Yoong, whose suggestions and knowledgable feedbacks have always been greatly appreciated. 
%Their continued efforts, together with EADS's various other contributions have greatly enhanced the quality of this research. 

Special thanks go to my friends and colleagues, whose friendship and companionship have made the journey a truly enjoyable one. 
They include but are not limited to: Brian Nguyen Quang Huy, Erwin Anggadjaja and Hamid Reza Sharifzadeh ...

Last but not least I would like to give my appreciation to all NTU staff in PDCC, SCE and GSO whose quiet but continuous supporting efforts played a very important role in any measure of success this dissertation may be associated with.

\begin{flushright}
	\parbox[t]{1\textwidth}{%b
	\begin{flushright}
		\emph{{}``The roots of education are bitter, but the fruit is sweet.''}\\
		\emph{--} Aristotle\\
	\par\end{flushright}%
	}	
\par\end{flushright}

%\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------
